Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and ...

### 2020-06-03 reports/article.Rmd
have re-run the analysis and adjusted graphs accordingly

---
title: "Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and ..."
author: Erik Bulow^1,2,3^, Ola Rolfson^1,2,3^, ...,  Nils P. Hailer^1,3^
date: '`r Sys.Date()`'
bibliography: H:/zotero_lib.bib
csl: the-lancet.csl
output: 
  bookdown::word_document2:
    reference_docx: article.dotx
    toc: false
    df_print: kable
---

@@

infection_data %>% 
  select(outcome, time, coefs_selected) %>% 
  mutate(coefs_selected = map(coefs_selected, "brlasso_tbl_selected")) %>% 
  unnest("coefs_selected") %>%
  filter(outcome == "infection") %>% 
  select(-outcome) %>% 
  pivot_wider(names_from = "time", values_from = "n") %>% 
  mutate(
    variable = clean_names(variable) %>% 
      {gsub("\\.", " ", .)} %>% 
      {gsub("Rheumatidisease", "Rheumatic disease", .)}
  ) %>% 
  select(Predictor = variable, `90 days` = `90d`, `2 years` = `2y`) %>% 
knitr::kable(
  caption = "Variables selected by the bootstrap ranking procedure, and therefore kept in the main model. Variables chosen at least 33 times out of 100 were kept in the reduced model as well. (BMI = body mass index. ASA class = American Society for Anesthesiologists classification. CNS = central nervous system.)")
```

>>>>

---
title: "Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and ..."
author: Erik Bulow^1,2,3^, Ola Rolfson^1,2,3^, ...,  Nils P. Hailer^1,3^
date: '`r Sys.Date()`'
bibliography: 
#  H:/zotero_lib.bib
  C:\\Users\\erik_\\Documents\\library.bib
csl: the-lancet.csl
output: 
  bookdown::word_document2:
    reference_docx: article.dotx
    toc: false
    df_print: kable
---

@@

infection_data %>% 
  select(outcome, time, coefs_selected) %>% 
  mutate(coefs_selected = map(coefs_selected, "brlasso_tbl_selected")) %>% 
  unnest("coefs_selected") %>%
  filter(outcome == "infection") %>% 
  select(-outcome) %>% 
  pivot_wider(names_from = "time", values_from = "n") %>% 
  mutate(
    variable = clean_names(variable) %>% 
      {gsub("\\.", " ", .)} %>% 
      {gsub("Rheumatidisease", "Rheumatic disease", .)} %>% 
      {gsub("Sex Male", "Male gender", .)}
  ) %>% 
  select(Predictor = variable, `90 days` = `90d`, `2 years` = `2y`) %>% 
knitr::kable(
  caption = "Variables selected by the bootstrap ranking procedure, and therefore kept in the main model. Variables chosen at least 33 times out of 100 were kept in the reduced model as well. (BMI = body mass index. ASA class = American Society for Anesthesiologists classification. CNS = central nervous system.)")
```
